Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-09 GWLDCII.tex
responding to some of Susama's questions in sec 5

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
\begin{itemize}
  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
    \begin{itemize}
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{-1}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set \hlfix{$I_{0} = I_n$}{changed. correct?}.)
	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
      \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.  %$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item Define $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}

\hlfix{That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{th}$.}{added. accurate?}

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $s$\todo{$s = r$ in pictures} to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
\]
The Grassmann necklace of this diagram is 
\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.

From $I_1$ to $I_2$, the propagators $p$ and $q$ change \hlfix{which vertex they are assigned to}{Can we change this language to which vertices they contribute?}. That is $I_1(p) = 1$, $I_1(q)= 2$ while $I_2(p) = 2$, $I_2(q)= 5$. However, $r$ contributes  4 to both $I_1$ and $I_2$, so $S_2 = \{p,q\}$.  Then
\[
\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ 1 & 1 & 1 \end{bmatrix} = gb.
\] {\color{violet} shouldn't $r_2$ be a $2 \times 2$ matrix? i.e. $r_2 = \det\begin{bmatrix} b & 0 \\ f &  g \end{bmatrix} = gb.$}
\hlfix{where the 1s in the third row of the second matrix correspond to the fact that $I_1(s) = I_2(s)$.}{This doesn't seem to match with what is said in the algorithm.}  Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.

At $I_7$ the situation \hlfix{is more complicated}{It seems to be exactly what we expect from the alg?}: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.

Note that unlike the previous $r_i$, $r_7$ an irriducible quadratic factor. This corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.

@@

\begin{proof}
\begin{enumerate}
    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.  Thus each $\Delta_{I_i}$ and each $r_i$ is homogeneous.  %Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.  Thus each $r_i$ is homogeneous.
    \item Using the expression for the determinant as a sum over permutations from Corollary~\ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.  The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.  Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.

@@

Expanding out $fg$ yields a signed sum of monomials. \hlfix{In each of these monomials, $f$ contributes those variables associated both to a propagator in $\mathcal{P}'$ and to a vertex in $J$, and $g$ contributes those variables associated both to a propagator not in $\mathcal{P}'$ and to a vertex not in $J$, and no other variables appear.  }{Isn't this redundant with the previous paragraph?}

Since there is no cancellation between terms, this means that the full expansion over permutations of $\Delta_{I_i}$ contains no other nonzero terms and hence no other variables.  Therefore $\Delta_{I_i}$ is equal to the determinant of the matrix obtained by taking the submatrix of $C(W)$ with columns indexed by $I_i$ and setting any variables not appearing in $\Delta_{I_i}$ to $0$.  This new matrix is, up to permutations of rows and columns, a block matrix with one block for $\mathcal{P}'$ and $J$ and the other block for the complements.  Thus its determinant, and hence also $\Delta_{I_i}$, is the product of the minors for these two blocks.  By considering which variables appear, these two factors must also be $f$ and $g$, and so in particular $f$ is the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$.  This proves the claim.

@@

All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.  Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$. Note that by removing the propagators which come \hlfix{before}{ordering?} those contributing to $f$ and \hlfix{changing $i$ to be the first vertex}{does this generalize to other $i$?} which contributes to $f$, we obtain a \hlfix{different admissible diagram}{Is this just the diagram gotten by removing certain props?} for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
$i$ contributes to $f$.  Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.  Finally, we can suppose that $W$ is minimal in number of propagators with the above occuring.

@@

If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which \hlfix{is a contradiction}{Why? because $i$ contributes to $f$?}.  So we must have at least one of $m$ and $m+1$ in $I_i$.  However, all propagators in $S$ are mapped by the function $I_{i}(\cdot)$ to vertices strictly before $m$, so the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.  Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.  If we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a smaller diagram for which $\Delta_{I_i} = \det A$ {\color{violet}why not $\det A \det C'$ with $C'$a minor of $C$?}. This contradicts the minimality of our choices unless $\det A$ is quadratic, which in turn contradicts our assumption that $i$ and $p$ contribute to an irreducible factor $f$ of degree at least 3.

\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.  If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.  Thus we can take $q$ to be the propagator such that $I_i(q)=i+1$. {\color{violet} How do we know this exists? Why can't we solve this by having $r$ supported on the $i-1^{th}$ edge?} We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).  Write $(i, i+1, j, j+1)$ for the support of $q$.  The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.

Similarly to Case 1, let \st{$S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.}{\color{violet}$S = \cP_{in}(q)$ in the $<_i$ order. Note that $p \in S$.}\hlfix{Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.}{???}  Thus the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the submatrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. Again two things can now happen.  If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.  This yields a contradiction as in Case 1: either $W$ contains unnecessary propagators which contradicts our minimality assumption, or $\det A$ is quadratic which contradicts the assumption that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.

@@

\item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$, with $I_i(p)=a$ and $I_i(q)=b$.  Let $x_{p,a},x_{p,b},x_{q,a},x_{q,b}$ be the associated variables in $C(W)$. For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.  The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of \hlfix{$x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$}{why? terms in determinant come from bijections. Why should all bijections appear in det?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.  Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.  Therefore no such terms exist and $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ is a factor of $\Delta_{I_i}$.

@@

{\color{violet} Got rid of need for scalar multiples by talking about radicals.}

@@

Finally then we need to check the scalar.  By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ deteriminant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.  Therefore $R=R(W)$. \todo{I'm pretty sure that there isn't a sign issue here. But do we have a proof?}
\end{proof}

>>>>

\begin{algorithm}\label{alg WLD to denom via GN}
Let $W = (\cP,n)$ be a Wilson loop diagram, and let $C(W)$ be the matrix of $W$ as defined in \eqref{C(W) dfn} with a fixed ordering on $\cP$. (see Section~\ref{section WLD background}).
\begin{itemize}
  \item For each $i \in [n]$, we construct a factor $r_i$ as follows:
    \begin{itemize}
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i-1$st Grassmann necklace element, $I_{i-1}$.  (By convention set $I_{0}=I_n$.)  Write $I_{i-1}(p)$ for the vertex associated to propagator $p$ under this bijection.
      %\item Use Algorithm~\ref{alg:put GN on WLD} to obtain a bijection between the propagators and the $i$th Grassmann necklace element, $I_{i}$.  Write $I_{i}(p)$ for the vertex associated to propagator $p$ under this bijection.
      \item Let $S_i = \{p \in \cP \ | \ I_{i-1}(p) \neq I_i(p)\}$. (By convention, set $I_{0} = I_n$.)
	  %\item Write $\Delta_{I_i}$ for the determinant of the $k \times k$ minor of $C(W)$ with columns indexed by $I_i$.
      \item Let $r_i$ be the determinant of the $|S_i|\times |S_i|$ minor of $C(W)$ with rows indexed by $S_i$ and columns indexed by $I_i(S_i)$.  %$\Delta_{I_i}$ with all variables from rows associated to $p\not\in S_i$ set to $1$.
    \end{itemize}
  \item Define $R = \prod_{i=1}^n r_i$.
\end{itemize}
\end{algorithm}

That is, each $r_i$ is the determinant of the minor determined by the propagators (rows) that contribute different values (columns) to the $i^{th}$ element of the Grassmann necklace than they did to the $i-1^{th}$.

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $r$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}
\]
The Grassmann necklace of this diagram is 
\begin{gather*}I_1 = \{1,2,4\}, I_2 = \{2,4,5\}, I_3 = \{4,5,6\}, I_4=\{4,5,6\},\\ I_5=\{5,6,7\}, I_6 = \{6,7,1\}, I_7=\{7,1,2\}. \end{gather*}  
Figure~\ref{fig R eg} indicates the pairings between propagators and vertices for each $i \in [1,7]$.

From $I_1$ to $I_2$, the propagators $p$ and $q$ change which vertices they contribute. That is $I_1(p) = 1$, $I_1(q)= 2$ while $I_2(p) = 2$, $I_2(q)= 5$. However, $r$ contributes  4 to both $I_1$ and $I_2$, so $S_2 = \{p,q\}$.  Then
\[
\Delta_{I_2}=\det\begin{bmatrix} b & 0 & 0 \\ f & 0 & g \\ j & k & l \end{bmatrix} = kgb, \qquad r_2 = \det\begin{bmatrix} b & 0 \\ f & g \end{bmatrix} = gb.
\] 
Continuing likewise, we get $r_3 = c$, $r_4=1$ (since $I_4 = I_3$), $r_5 = lhd$, and $r_6 = i$.

At $I_7$ the situation we see for the first time an irreducible quadratic factor: we have $S_7 = \{q,s\}$ with $I_7(S_7) = \{ 1,2\}$, $\Delta_{I_7} = d(ej-fi)$ and $r_7 = ej-fi$.

The irriducible quadratic factor corresponds to the fact that $q$ and $s$ share an edge {\em and} contribute both endpoints of that edge to $I_7$; see Proposition~\ref{prop alg gives rad} below.

@@

\begin{proof}
\begin{enumerate}
    \item The nonzero entries of $C(W)$ are independent indeterminates and so every $i\times i$ minor of $C(W)$ is either homogeneous of degree $i$ or is $0$.  Thus each $\Delta_{I_i}$ and each $r_i$ is homogeneous.  %Furthermore, each row contributes one factor to each term in the expansion of $\Delta_{I_i}$ so the result of setting the variables from a subset of rows to $1$ is still homogeneous.  Thus each $r_i$ is homogeneous.
    \item Using the expression for the determinant as a sum over permutations along with Corollary~\ref{lem basis as perm} we see that $\Delta_{I_i}$ is a sum over bijections between $I_i$ and $\mathcal{P}$.  The nonzero terms in this sum are precisely those bijections such that each propagator is associated to one of its supporting vertices in $I_i$, since only those locations in $C(W)$ are nonzero.  Since the nonzero entries of $C(W)$ are independent there can be no cancellation between terms in this expansion.

@@

Expanding out $fg$ yields a signed sum of monomials. Since there is no cancellation between terms, this means that the full expansion over permutations of $\Delta_{I_i}$ contains no other nonzero terms and hence no other variables.  Therefore $\Delta_{I_i}$ is equal to the determinant of the matrix obtained by taking the submatrix of $C(W)$ with columns indexed by $I_i$ and setting any variables not appearing in $\Delta_{I_i}$ to $0$.  This new matrix is, up to permutations of rows and columns, a block matrix with one block for $\mathcal{P}'$ and $J$ and the other block for the complements.  Thus its determinant, and hence also $\Delta_{I_i}$, is the product of the minors for these two blocks.  By considering which variables appear, these two factors must also be $f$ and $g$, and so in particular $f$ is the minor of $C(W)$ associated to $\mathcal{P}'$ and $J$.  This proves the claim.

@@

All that remains is to prove that $\Delta_{I_i}$ has no irreducible factors of degree 3 or more.  Suppose for a contradiction that $f$ is a factor of $\Delta_{I_i}$ of degree $\geq 3$. Note that by removing the propagators which come before those contributing to $f$ in the order given by the construction of $I_i$ and \hlfix{changing $i$ to be the first vertex}{does this generalize to other $i$?} which contributes to $f$, we obtain a \hlfix{different admissible diagram}{Is this just the diagram gotten by removing certain props?} for which $f$ still divides $\Delta_{I_i}$ but also $i\in I_i$ and
$i$ contributes to $f$. \note{The point of all the stuff you were objecting to is just to spell out ``WLOG we may assume $i\in I_i$ and $i$ contributes to $f$''.  How do you want that said?} Showing that this different admissible diagram gives a contradiction is sufficient, and so we may assume that $i\in I_i$ and $i$ contributes to $f$.  Finally, we can suppose that $W$ is minimal in number of propagators with an irreducible factor of degree $\geq 3$.

@@

If neither $m$ nor $m+1$ appear in $I_i$ then by Corollary~\ref{no coloops} $V(p) \cap I_i = \{i\}$, and so the row of $p$ in the matrix of $\Delta_{I_i}$ has only one nonzero entry; hence $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$, which is a contradiction to the fact that $i$ contributes to $f$.  So we must have at least one of $m$ and $m+1$ in $I_i$.  However, all propagators in $S$ are mapped by the function $I_{i}(\cdot)$ to vertices strictly before $m$, so the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the $|S|\times |S|$ matrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. No other propagators can be supported on these vertices since all other propagators are outside of $p$, and $p$ is the first propagator supported at $i$; this explains the zero block.  Therefore $\Delta_{I_i} = \det A \det C$, and both factors are nontrivial since at least one of $m$ and $m+1$ appear in $I_i$.  Since $p\in \cP_{in}(p)$ we have $f|\det A$ and if we remove the propagator outside of $p$ that contributes $m$ or $m+1$, we get a diagram with fewer propagators for which $\det A | \Delta_{I_i}$.  This contradicts the minimality of our choices.

\textbf{Case 2}: Suppose $p$ has one end on the edge $(i, i+1)$.  If no other propagators are supported on $i$ then the column of $C(W)$ corresponding to vertex $i$ has only one nonzero entry in it, and so $\Delta_{I_i}$ has a linear factor contributed by $p$ and $i$; as above, this is a contradiction.  Thus there is at least one other propagator on edge $(i,i+1)$ since since $I_i(p)=i$, one of these other propagators contributes $i+1$ in $I_i$, sob we can take $q$ to be the propagator such that $I_i(q)=i+1$. {\color{violet} How do we know this exists? Why can't we solve this by having $r$ supported on the $i-1^{th}$ edge?}\note{I tried to clarify what $q$ is and why it exists, but I don't know what $r$ is in your question.} We know that $q$ has one end on the edge $(i, i+1)$ and is adjacent to $p$ on that edge in the counterclockwise direction (see Figure \ref{fig no big factors}).  Write $(i, i+1, j, j+1)$ for the support of $q$.  The situation for $q$ is very similar to case 1: in particular, we have $I_{i+1}(q) = j$ by Lemma~\ref{vertex cyclic int lem} and so if $j\in I_i$ then the propagator which contributes $j$ is outside of $q$.

Similarly to Case 1, let \st{$S$ be the set of propagators inside $q$ along with $p$ and $q$ themselves.}{\color{violet}$S = \cP_{in}(q)$ in the $<_i$ order. Note that $p \in S$.}\note{No, $S=\cP_{in}(q)\cup \{p\}$ in the $<_i$ order because $q$ is not inside $p$ in that order}\hlfix{Then all propagators in $S$ are mapped by $I_i(\cdot)$ to vertices strictly before $j$ and no other propagators are supported on vertices strictly before $j$.}{???} \note{This is the usual argument...} Thus the matrix giving $\Delta_{I_i}$ has the form
\[
\begin{bmatrix} A & B \\ 0 & C\end{bmatrix}
\]
where $A$ is the submatrix indexed by the propagators in $S$ and the vertices in $I_i(S)$. Again two things can now happen.  If some vertex $j$ or larger (with respect to $>_i$) belongs to $I_i$ then $B$ and $C$ are at least one column wide, and so the block form of the matrix gives a nontrivial factorization of $\Delta_{I_i}$.  This yields a contradiction as in Case 1: either $W$ contains unnecessary propagators which contradicts our minimality assumption, or $\det A$ is quadratic which contradicts the assumption that $p$ and $i$ contribute to $f$, an irreducible factor of degree at least 3.

@@

\item Suppose propagators $p$ and $q$ are supported on a common edge $(a,b)$, with $I_i(p)=a$ and $I_i(q)=b$.  Let $x_{p,a},x_{p,b},x_{q,a},x_{q,b}$ be the associated variables in $C(W)$. For any fixed bijection $\sigma$ from $\cP-\{p,q\}$ to $I_i -\{a,b\}$ for which each propagator is supported on its image under the bijection, we can extend $\sigma$ to a bijection of all propagators with $I_i$ in two ways: either $p\mapsto a$ and $q\mapsto b$ or $p\mapsto b$ and $q\mapsto a$.  The sum of the contributions of all these bijections to $\Delta_{I_i}$ is therefore the product of \hlfix{$x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$}{why? terms in determinant come from bijections. Why should all bijections appear in det?}\note{All terms appear by the permuation form of the determinant -- am I mising what you're asking?} with the minor coming from $\cP-\{p, q\}$ and $I_i - \{a,b\}$.  Since there is no cancellation of terms in the expansion of $\Delta_{I_i}$, if any other terms appear then they will cause a factor which is not in the form described in the previous part.  Therefore no such terms exist and $x_{p,a}x_{q,b}-x_{p,b}x_{q,a}$ is a factor of $\Delta_{I_i}$.

@@

@@

Finally then we need to check the scalar.  By Definition~\ref{def R(W)} each linear factor appears with coefficient $1$ and each $2\times 2$ deteriminant factor appears with the same sign as the determinant of the corresponding minor in $C(W)$.  Therefore $R=R(W)$. \todo{I'm pretty sure that there isn't a sign issue here. But do we have a proof?}\note{The previous sentence is the proof -- again I think I'm missing something in your question}
\end{proof}
